\documentclass[12pt]{extarticle}

\usepackage{enumitem}
\usepackage{verbatim}
\usepackage[left=30pt,right=30pt,top=30pt,bottom=30pt]{geometry}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{tabularx}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontspec}
\usepackage[T1]{fontenc}

\definecolor{Purple}{HTML}{3E0097}

\setmainfont[
  BoldFont={Fira Sans Medium},
  ItalicFont={Fira Sans Light Italic}
]{Fira Sans Book}

\pagenumbering{gobble}
\titlespacing*{\section}{0pt}{7pt}{7pt}
\titlespacing*{\subsection}{0pt}{7pt}{0pt}
\titleformat{\section}{\color{Purple}\large\bfseries}{}{}{}[\titlerule]
\titleformat{\subsection}[runin]{\normalfont\Large\bfseries}{}{}{}

\setlist[itemize]{noitemsep,leftmargin=20pt}
\setlength{\parskip}{0em}

\begin{document}

\begin{center}
\textbf{\huge{Zachary Batten}}

St.John's, NL, Canada
$\bullet$ \href{mailto:me@zacbatten.com}{me@zacbatten.com}
$\bullet$ 709--691--2022
$\bullet$ \href{https://zacbatten.com}{zacbatten.com}
\end{center}

\section*{Education}
\subsection*{\href{https://www.mun.ca/}{Memorial University of Newfoundland} 
}
\hfill \textbf{Jan. 2019 to Current}

B. Science, Computer Science Major

\section*{Experience}

\subsection*{\href{https://muncompsci.ca/}{Event Coordinator} 
}
\hfill \textbf{Sept. 2020 to Sept. 2022}

\textit{Computer Science Society}
\begin{itemize}
  \item Coordinated a range of events aimed at fostering relationships between students.
  \item Spearheaded workshops and game nights tailored for Computer Science students.
  \item Engaged in bi-weekly executive meetings to determine the society's future direction and event planning
\end{itemize}

\subsection*{\href{https://hackfrostnl.ca/}{Logistics Lead}
} \hfill \textbf{Oct. 2020 to Feb. 2022}

\textsl{Hack Frost NL}
\begin{itemize}
  \item Instrumental in the formative stages of the organization, contributing ideas and strategic insights.
  \item Led a dedicated team to successfully manage the logistics for the inaugural and subsequent hackathons (2021 and 2022).
  \item Established and monitored weekly goals to ensure smooth team operations.
  \item Collaborated with external partners to source products and services vital for the hackathons.
  \item Continuously updated the Hack Frost website to keep participants informed and engaged.
\end{itemize}

\section*{Projects}

\subsection*{\href{https://github.com/Inefy/NovaStar}{NovaStar}
} \hfill
\begin{itemize}
\item Designed an AI agent that plays StarCraft II using Deep Q-Learning Network (DQN).
\item Enhanced the standard DQN with Dueling architecture, improving learning efficiency and stability.
\item Designed the agent to interact with the environment, store experiences, update policies, and synchronize networks.

\end{itemize}

\subsection*{\href{https://github.com/Inefy/MuseGenAI}{MuseGenAI}
} \hfill
\begin{itemize}
	\item Developed a dynamic Music Generator, leveraging OpenAI's GPT-4, GPT-3, and GPT-3 Turbo AI engines.
	\item Users can customize music generation, choosing style, genre, number of notes, and instruments.
	\item Creativity of the music is adjustable via a temperature slider, adding a unique layer of customization.
	\item Generated music can be saved as MIDI files and played directly within the app.
	\item The application is constructed with React.js (frontend), Flask (backend).
\end{itemize}
	



\subsection*{\href{https://technl.ca/2022/07/28/techfwd-conclusion/}{Patio Teams}
} \hfill

\textsl{techNL Hackathon}
\begin{itemize}
	\item Led the team to first place victory through effective collaboration and strategic planning.
  \item Pioneered the project idea, gaining unanimous support from team members.
  \item Co-produced the project and presented a social media app designed to facilitate collaborations among developers.
\end{itemize}

\section*{Technical Skills}
\begin{itemize}
  \item \textbf{Language experience}: Python, Javascript, C\texttt{++}, Java
  \item \textbf{Libraries \& Framework}: Flask, Node.js, Pandas, JUnit, Scrapy, React
  \item \textbf{Technologies \& Tools}: AWS, PostgreSQL, Windows, Docker, and Linux.
  

\end{itemize}

\end{document}
